5'CutSiteAnalysisDataGeneration

### 2023-07-31 R/CutSiteCorrelationDataGeneration.rmd
Added species for cut site correlation analysis
Added Arabidopsis and yeast

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1MismatchesByReadDirectory = file.path(deaminationDataDirectory, "NHF1", "mismatches_by_read")
NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
dir.create(NHF1CutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
```

@@

```{r generate_cut_site_correlation_data}
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory)
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T", filteredAndFormattedInput = FALSE,
                                         filePathIncludedMismatches = character())
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)
```

>>>>

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1MismatchesByReadDirectory = file.path(deaminationDataDirectory, "NHF1", "mismatches_by_read")
NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
arabidopsisMismatchesByReadDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "mismatches_by_read")
arabidopsisCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "cut_site_correlation")
yeastMismatchesByReadDirectory = file.path(deaminationDataDirectory, "yeast", "mismatches_by_read")
yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
dir.create(NHF1CutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
dir.create(arabidopsisCutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
dir.create(yeastCutSiteCorrelationDirectory, showWarnings = FALSE, recursive = TRUE)
```

@@

```{r generate_cut_site_correlation_data}
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory)
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T")
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "C>T", filteredAndFormattedInput = FALSE,
                                         filePathIncludedMismatches = character())
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "1h", "NHF1",
                                         NHF1MismatchesByReadDirectory, NHF1CutSiteCorrelationDirectory,
                                         includedMismatches = "CC>TT", filteredAndFormattedInput = FALSE)

cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "ZT2", "Arabidopsis",
                                         arabidopsisMismatchesByReadDirectory, arabidopsisCutSiteCorrelationDirectory)
cutSiteCorrelationAnalysisDataGeneration("CPD", "all_reps", "20min", "yeast",
                                         yeastMismatchesByReadDirectory, yeastCutSiteCorrelationDirectory)
```

### 2023-07-31 R/CutSiteCorrelationFigureGeneration.rmd
Added species for cut site correlation analysis
Added Arabidopsis and yeast

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
```

@@

```{r generate_cut_site_correlation_figures}
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T", filteredAndFormattedInput = FALSE)
```

>>>>

deaminationDataDirectory = file.path(bioinformaticsDirectory, "deamination_determination", "data")
NHF1CutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "NHF1", "cut_site_correlation")
arabidopsisCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "Arabidopsis", "cut_site_correlation")
yeastCutSiteCorrelationDirectory = file.path(deaminationDataDirectory, "yeast", "cut_site_correlation")
```

@@

```{r generate_cut_site_correlation_figures}
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           filteredAndFormattedInput = FALSE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T", filteredAndFormattedInput = FALSE)

cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisCutSiteCorrelationDirectory)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "20min", "yeast", yeastCutSiteCorrelationDirectory)
```
